\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Project 2 Proposal Programming II}
\author{Morgan Nihlmar}
\date{April 2024}

\begin{document}

\maketitle
\hrule
\section{Introduction}
I want to create a Fitness Routine Logger application. Basically, users can create routines for themselves which they can then select and create a log for each session of the routine that they do. They will have the routine as a base template but can then state whether they did less than expected sets/repetitions/exercises, and they will also log the weight that they lifted which can then be used to see how much they improve over time. There will be the option for users to compare statistics between each other as well as the feature of seeing your own improvement. 
\vspace{0.1cm}
\hrule

\section{Technologies Used}
\begin{itemize}
    \item Python
    \item Django - For the inbuilt user creation and management, as well as the ORM system to interact with the database
    \item JS, HTML, CSS, Bootstrap - Potentially for the front-end
    \item Git - For version control
\end{itemize}
\hrule


\section{Project Details}
To clarify what features the app will have: 
\begin{itemize}
    \item The ability for users to create and edit routines which are stored in a database tied to the user.
    \item Log workouts based off the routine templates, stating your performance and any adjustments you made in the session which will also be stored for a later comparison.
    \item Data analysis of your improvements/stagnation/regression in your routines over time (and potentially comparison between users). There will be several ways that this data is displayed.
\end{itemize}


\end{document}
